Towards clustering mutants to meet CI/CD timelines

### 2022-01-25 mutation-workshop/paper.tex
fixed tables

\author{
\IEEEauthorblockN{Rasjaad Basarat}
\IEEEauthorblockA{\textit{Software Engineering Master} \\ %% TODO: CHANGE THIS
\textit{University of Amsterdam}\\
Amsterdam, the Netherlands \\
rasjaad@nivero.io}

\and
\IEEEauthorblockN{Ana Oprescu}
\IEEEauthorblockA{\textit{Complex Cyber Infrastructure} \\
\textit{University of Amsterdam}\\
Amsterdam, the Netherlands \\
a.m.oprescu@uva.nl}
\and
\IEEEauthorblockN{Thomas Biesaart}
\IEEEauthorblockA{\textit{} \\ %% TODO: CHANGE THIS
Amsterdam, the Netherlands \\
thomas.biesaart@protonmail.com}
}

@@

\section{Results}
\label{ch:results}
% In this chapter we present the results of our experiments.
We divide the results in two sections. The first section presents the results of clustering with hierarchical clustering. The second section presents the results of clustering with the fuzzy c-means model.
We select the Levenshtein distance for our similarity characteristic\cite{thesis}.
While extracting the set of characteristics (Section~\ref{ch:identifying_characteristics}, we observed that calculating the Levenshtein distance is computationally expensive.
% Calculating the Levenshtein distance for the four biggest projects in the data set cost days\cite{thesis}.
% Even for the smaller projects the extraction of the characteristics cost hours\cite{thesis}.
Including the Levenshtein distance defeats the purpose of increasing performance as every bit of performance we gain would be replaced by the cost of calculating the Levenshtein distance~\cite{thesis}.
All results displayed are in percentages and ms=mutation score, ca=cluster accuracy.

\subsection{Hierarchical clustering}
We present the results of our clustering algorithm when executed without the Levenshtein distance.
The results are grouped based on the reduced percentage of mutants executed.
We also display the accuracy of the clusters per reduction amount.
The data we present are the average of the results of the 30 repetitions of the experiment.
The result of each single repetition can be found in our Github repository in the folder\textit{experiment{\_}results}~\cite{rbasarat-repo}.

@@

\begin{tabular}{|l|c|c|c|c|c|}

@@

\multicolumn{1}{|c|}{Project} & \begin{tabular}[c]{@{}c@{}}ms\\ full set\end{tabular} & \begin{tabular}[c]{@{}c@{}}ms \\ clustered set\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg. ca\end{tabular} & \begin{tabular}[c]{@{}c@{}}Min. ca\end{tabular} & \begin{tabular}[c]{@{}c@{}}ca\end{tabular} \\ \hline
Google Auto Service           & 0.00                                                                                  & 0.00                                                                                      & 0.00                                                                               & 0.00                                                                                & 0.00                                                                               \\ \hline
ScribeJava-Core               & 33.52                                                                                 & 33.72                                                                                     & 92.24                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Auto Factory           & 48.41                                                                                 & 48.32                                                                                     & 94.21                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Auto Common            & 59.59                                                                                 & 60.03                                                                                     & 91.19                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Auto Value             & 61.42                                                                                 & 62.58                                                                                     & 93.90                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Gson                   & 66.83                                                                                 & 66.89                                                                                     & 91.75                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-io                    & 69.70                                                                                 & 66.08                                                                                     & 90.20                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-cli                   & 79.07                                                                                 & 78.97                                                                                     & 91.11                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-text                  & 79.29                                                                                 & 79.30                                                                                     & 90.95                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-codec                 & 84.56                                                                                 & 84.59                                                                                     & 94.56                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-csv                   & 85.16                                                                                 & 85.24                                                                                     & 92.76                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline

@@

\caption{\label{tab:clustering_no_distance_25}Results of clustering mutants without Levensthein distance and cluster size n*0.25}

@@

Figure \ref{box:clustering_no_distance_25} displays the box-plots of the weighted mutation score obtained from each individual sample.
We observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table~\ref{tab:clustering_no_distance_25} displays the results of clustering mutants without Levensthein distance and the number of clusters equal to the total amount of mutants * 0.25. 
We observe that the maximum and minimum differences in mutation score between a full set and a clustered set  3.61\%, and 0.09\%, respectively.
The average of the differences between full set score and clustered score is 0.53\%.

@@

\multicolumn{1}{|c|}{Project} & \begin{tabular}[c]{@{}c@{}}ms\\ full set\end{tabular} & \begin{tabular}[c]{@{}c@{}}ms \\ clustered set\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg. ca\end{tabular} & \begin{tabular}[c]{@{}c@{}}Min. ca\end{tabular} & \begin{tabular}[c]{@{}c@{}}ca\end{tabular} \\ \hline
Google Auto Service           & 0.00                                                                                  & 0.00                                                                                      & 0.00                                                                               & 0.00                                                                                & 0.00                                                                               \\ \hline
ScribeJava-Core               & 33.52                                                                                 & 33.55                                                                                     & 97.16                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Auto Factory           & 48.41                                                                                 & 48.44                                                                                     & 97.71                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Auto Common            & 59.59                                                                                 & 59.86                                                                                     & 96.35                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Auto Value             & 61.42                                                                                 & 62.62                                                                                     & 97.31                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Gson                   & 66.83                                                                                 & 66.81                                                                                     & 95.29                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-io                    & 69.70                                                                                 & 66.05                                                                                     & 95.08                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-cli                   & 79.07                                                                                 & 78.97                                                                                     & 95.55                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-text                  & 79.29                                                                                 & 79.30                                                                                     & 95.34                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-codec                 & 84.56                                                                                 & 84.59                                                                                     & 96.95                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-csv                   & 85.16                                                                                 & 85.11                                                                                     & 95.87                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline

@@

\caption{\label{tab:clustering_no_distance_50}Results of clustering mutants without Levensthein distance and cluster size n*0.50}

@@

Figure~\ref{box:clustering_no_distance_50} displays the box-plots of the weighted mutation score obtained from each individual sample. 
We observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table~\ref{tab:clustering_no_distance_50} displays the results of clustering mutants without Levensthein distance and the number of clusters equal to the total amount of mutants * 0.50.
The maximum and minimum differences between the score of a full set and clustered set are 3.65\%, and 0.03\%, respectively.
We observe that the average cluster accuracy is higher than the average cluster accuracy of the 25\% set. 
The average of the differences between full set score and clustered score is 0.49\% which is smaller than the average difference than that of the 25\% set.

@@

\begin{tabular}{|l|c|c|c|c|c|}
\multicolumn{1}{|c|}{Project} & \begin{tabular}[c]{@{}c@{}}ms\\ full set\end{tabular} & \begin{tabular}[c]{@{}c@{}}ms \\ clustered set\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg. ca\end{tabular} & \begin{tabular}[c]{@{}c@{}}Min. ca\end{tabular} & \begin{tabular}[c]{@{}c@{}}ca\end{tabular} \\ \hline
Google Auto Service           & 0.00                                                                                  & 0.00                                                                                      & 0.00                                                                               & 0.00                                                                                & 0.00                                                                               \\ \hline
ScribeJava-Core               & 33.52                                                                                 & 33.48                                                                                     & 98.63                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Auto Factory           & 48.41                                                                                 & 48.34                                                                                     & 98.41                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Auto Common            & 59.59                                                                                 & 59.71                                                                                     & 97.08                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Auto Value             & 61.42                                                                                 & 62.66                                                                                     & 97.99                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
Google Gson                   & 66.83                                                                                 & 66.84                                                                                     & 97.37                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-io                    & 69.70                                                                                 & 66.07                                                                                     & 97.34                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-cli                   & 79.07                                                                                 & 79.12                                                                                     & 96.83                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-text                  & 79.29                                                                                 & 79.33                                                                                     & 97.60                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-codec                 & 84.56                                                                                 & 84.61                                                                                     & 98.43                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
commons-csv                   & 85.16                                                                                 & 85.07                                                                                     & 97.49                                                                              & 50.00                                                                               & 100.00                                                                             \\ \hline
\caption{\label{tab:clustering_no_distance_75}Results of clustering mutant without Levensthein distance and cluster size n*0.75}

Figure~\ref{box:clustering_no_distance_75} displays the box-plots of the weighted mutation score obtained from each individual sample. 
We observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table~\ref{tab:clustering_no_distance_75} displays the results of clustering mutants without Levensthein distance and the number of clusters equal to the total amount of mutants * 0.50.
The maximum and minimum differences between the score of a full set and clustered set are 3.63\%, and 0.04\%, respectively.
We observe that the average accuracy is higher than the average accuracy of the other sets.
The average of the differences between full set score and clustered score is  0.49\% which is higher than the average difference than that of the 25\% and the same of that of the 50\% set.

>>>>

\author{
\IEEEauthorblockN{Rasjaad Basarat}
\IEEEauthorblockA{\textit{Software Engineering Master} \\ %% TODO: CHANGE THIS
\textit{University of Amsterdam}\\
Amsterdam, the Netherlands \\
rasjaad@nivero.io}
\and
\IEEEauthorblockN{Jelle Mouissie}
\IEEEauthorblockA{\textit{Informatics Institute} \\ %% TODO: CHANGE THIS
\textit{University of Amsterdam}\\
Amsterdam, the Netherlands \\
jelle.mouissie@xs4all.nl}
\and
\IEEEauthorblockN{Thomas Biesaart}
\IEEEauthorblockA{\textit{} \\ %% TODO: CHANGE THIS
Amsterdam, the Netherlands \\
thomas.biesaart@protonmail.com}
\and
\IEEEauthorblockN{Ana Oprescu}
\IEEEauthorblockA{\textit{Complex Cyber Infrastructure} \\
\textit{University of Amsterdam}\\
Amsterdam, the Netherlands \\
a.m.oprescu@uva.nl}
}

@@

\section{Results}
\label{ch:results}
% In this chapter we present the results of our experiments.
We divide the results in two sections. The first section presents the results of clustering with hierarchical clustering. The second section presents the results of clustering with the fuzzy c-means model.
We select the Levenshtein distance for our similarity characteristic\cite{thesis}.
While extracting the set of characteristics (Section~\ref{ch:identifying_characteristics}, we observed that calculating the Levenshtein distance is computationally expensive.
% Calculating the Levenshtein distance for the four biggest projects in the data set cost days\cite{thesis}.
% Even for the smaller projects the extraction of the characteristics cost hours\cite{thesis}.
Including the Levenshtein distance defeats the purpose of increasing performance as every bit of performance we gain would be replaced by the cost of calculating the Levenshtein distance~\cite{thesis}.

\subsection{Hierarchical clustering and more}
We present the results of our clustering algorithm when executed without the Levenshtein distance.
The results are grouped based on the reduced percentage of mutants executed.
We also display the accuracy of the clusters per reduction amount.
The data we present are the average of the results of the 30 repetitions of the experiment.
The result of each single repetition can be found in our Github repository in the folder\textit{experiment{\_}results}~\cite{rbasarat-repo}.
We compare the cluster accuracy of hierarchical clustering with different clustering algorithms, the results can be found in Table \ref{tab:clustering_extra}. 
Due to a limitation of resources the results only include the 75\% reduction variant of the experiment.
We can observe that hierarchical clustering has the smallest deviation in cluster accuracy compared to the other clustering algorithms.

@@

\begin{tabular}{|l|c|c|c|c|c|c|c|}

@@

\multicolumn{1}{|c|}{Project} & \begin{tabular}[c]{@{}c@{}}ms.\\ full set\end{tabular} & \begin{tabular}[c]{@{}c@{}}ms.\\ clustered set\end{tabular} & Min. ca. & max. ca. & \begin{tabular}[c]{@{}c@{}}Avg. ca.\\ size*0.25\end{tabular} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Avg. ca.\\ size*0.50\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Avg. ca.\\ size*0.75\end{tabular}} \\ \hline
Google Auto Service           & 0.00                                                   & 0.00                                                        & 0.00     & 0.00     & 0.00                                                           & 0.00                                                                              & 0.00                                                                              \\ \hline
ScribeJava-Core               & 33.52                                                  & 33.72                                                       & 50.00    & 100.00   & 92.24                                                          & 97.16                                                                             & 98.63                                                                             \\ \hline
Google Auto Factory           & 48.41                                                  & 48.32                                                       & 50.00    & 100.00   & 94.21                                                          & 97.71                                                                             & 98.41                                                                             \\ \hline
Google Auto Common            & 59.59                                                  & 60.03                                                       & 50.00    & 100.00   & 91.19                                                          & 96.35                                                                             & 97.08                                                                             \\ \hline
Google Auto Value             & 61.42                                                  & 62.58                                                       & 50.00    & 100.00   & 93.90                                                          & 97.31                                                                             & 97.99                                                                             \\ \hline
Google Gson                   & 66.83                                                  & 66.89                                                       & 50.00    & 100.00   & 91.75                                                          & 95.29                                                                             & 97.37                                                                             \\ \hline
commons-io                    & 69.70                                                  & 66.08                                                       & 50.00    & 100.00   & 90.20                                                          & 95.08                                                                             & 97.34                                                                             \\ \hline
commons-cli                   & 79.07                                                  & 78.97                                                       & 50.00    & 100.00   & 91.11                                                          & 95.55                                                                             & 96.83                                                                             \\ \hline
commons-text                  & 79.29                                                  & 79.30                                                       & 50.00    & 100.00   & 90.95                                                          & 95.34                                                                             & 97.60                                                                             \\ \hline
commons-codec                 & 84.56                                                  & 84.59                                                       & 50.00    & 100.00   & 94.56                                                          & 96.95                                                                             & 98.43                                                                             \\ \hline
commons-csv                   & 85.16                                                  & 85.24                                                       & 50.00    & 100.00   & 92.76                                                          & 95.87                                                                             & 97.49                                                                             \\ \hline

@@

\caption{\label{tab:clustering_no_distance}Results of clustering mutants with hierarchical clustering where and ms=mutation score in \%, ca=cluster accuracy in \% and size the total amount of mutants generated.}

@@

@@

\multicolumn{1}{|c|}{Project} & \begin{tabular}[c]{@{}c@{}}Ms. \\ full set\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg. ca.\\ random\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg. ca.\\ K-means\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg. ca.\\ Birch\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg. ca.\\ DBScan\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg. ca.\\ Optics\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg. ca.\\ MeanShift\end{tabular} \\ \hline
Google Auto Service           & 0.00                                                  & 0.00                                                    & 0.00                                                     & 0.00                                                   & 0.00                                                    & 0.00                                                    & 0.00                                                       \\ \hline
ScribeJava-Core               & 33.52                                                 & 76.65                                                   & 93.21                                                    & 93.26                                                  & 90.91                                                   & 92.09                                                   & 94.51                                                      \\ \hline
Google Auto Factory           & 48.41                                                 & 72.56                                                   & 94.36                                                    & 94.20                                                  & 91.41                                                   & 92.22                                                   & 95.00                                                      \\ \hline
Google Auto Common            & 59.76                                                 & 73.89                                                   & 91.09                                                    & 91.12                                                  & 87.36                                                   & 88.09                                                   & 93.73                                                      \\ \hline
Google Auto Value             & 62.68                                                 & 75.27                                                   & 94.23                                                    & 94.33                                                  & 90.59                                                   & 91.77                                                   & 94.90                                                      \\ \hline
Google Gson                   & 66.84                                                 & 76.56                                                   & 91.77                                                    & 91.62                                                  & 87.93                                                   & 88.30                                                   & 93.03                                                      \\ \hline
commons-io                    & 65.47                                                 & 76.08                                                   & 90.73                                                    & 90.43                                                  & 86.26                                                   & 87.39                                                   & 92.73                                                      \\ \hline
commons-cli                   & 79.10                                                 & 83.32                                                   & 91.36                                                    & 91.36                                                  & 86.85                                                   & 87.88                                                   & 92.77                                                      \\ \hline
commons-text                  & 79.33                                                 & 83.48                                                   & 90.28                                                    & 89.95                                                  & 86.30                                                   & 87.11                                                   & 91.96                                                      \\ \hline
commonc-codec                 & 84.61                                                 & 87.08                                                   & 94.46                                                    & 94.44                                                  & 92.08                                                   & 91.69                                                   & 95.41                                                      \\ \hline
commons-csv                   & 85.07                                                 & 87.28                                                   & 92.26                                                    & 92.08                                                  & 87.95                                                   & 89.65                                                   & 93.10                                                      \\ \hline

@@

\caption{\label{tab:clustering_extra}Results of clustering mutants with different clustering algorithms where and ms=mutation score in \%, ca=cluster accuracy in \%}

@@

Figure \ref{box:clustering_no_distance_25}, \ref{box:clustering_no_distance_50}, \ref{box:clustering_no_distance_75} displays the box-plots of the weighted mutation score obtained from each individual sample.
We observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table~\ref{tab:clustering_no_distance} displays the results of clustering mutants 
We observe that the maximum differences in mutation score between a full set and a clustered set are 3.61\%, 3.65\% and 3.63\% with a reduction of 75\%, 50\% and 25\% respectively.
We observe that the minimum differences in mutation score between a full set and a clustered set are 0.49\%, 0.03\% and 10.04\%  with a reduction of 75\%, 50\% and 25\% respectively.
The average of the differences between full set score and clustered score are 0.58\% 0.49\%, 0.49\% with a reduction of 75\%, 50\% and 25\% respectively.

@@
